---
title: "{{TITLE}}"
subtitle: "{{ANALYSIS_TYPE}}"
author: "{{AUTHOR}}"
date: "{{DATE}}"
format:
  html:
    toc: true
    toc-depth: 3
    number-sections: true
    embed-resources: true
    css: styles/qa-report.css
  docx:
    toc: true
    toc-depth: 3
    number-sections: true
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
execute:
  echo: false
  warning: false
  message: false
params:
  data_path: "{{DATA_PATH}}"
  process: "{{PROCESS}}"
  report_revision: "{{REVISION}}"
---

```{r}
#| label: setup
#| include: false
options(width = 100)
set.seed(123)
```

# Executive Summary

**Decision:** Replace this with the QA decision.

**Key evidence:** Replace this with the most important results.

**Recommended action:** Replace this with the operational next step.

# Scope And Objective

- Process or product: `r params$process`
- Analysis type: {{ANALYSIS_TYPE}}
- Report revision: `r params$report_revision`
- Data source: `r params$data_path`

# Data Readiness

```{r}
#| label: data-readiness-placeholder
if (nzchar(params$data_path) && file.exists(params$data_path)) {
  data <- read.csv(params$data_path, stringsAsFactors = FALSE)
  data.frame(
    rows = nrow(data),
    columns = ncol(data),
    missing_cells = sum(is.na(data))
  )
} else {
  data.frame(
    note = "No data file was loaded. Replace this section with the data readiness checks."
  )
}
```

# Method

Document the method, package selection, assumptions, and why the method fits the QA question.

# Results

Insert the main tables and figures here.

```{r}
#| label: example-plot
#| fig-cap: "Example placeholder figure. Replace with analysis output."
plot(cars$speed, cars$dist, pch = 19, col = "#1F5A7A",
     xlab = "Speed", ylab = "Distance")
```

# QA Interpretation

Translate statistical results into process meaning, risk, and action.

# Risks And Limitations

- Document missing information.
- Document assumption failures.
- Document sample size or data-quality limitations.
- Document whether MSA, stability, or confirmation is still needed.

# Actions And Follow-Up

| Action | Owner | Due Date | Evidence |
|---|---|---|---|
| Replace with action | TBD | TBD | TBD |

# Reproducibility

```{r}
#| label: session-info
sessionInfo()
```
